\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-07-06 doc/USER_MANUAL/manual_SPECFEM3D.tex
updates version tag to v2.0.2 in manual
updates code file version numbers to version 2.1

\author{$\copyright$ Princeton University (USA) and\\
University of Pau / CNRS / INRIA (France)\\
Version 2.0 \\
"Sesame"}

@@

\noindent
If you use this new version 2.0, which has non blocking MPI for much better performance for medium or large runs, please cite at least one of these six articles,
in which results of non blocking MPI runs are presented: \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

@@

The SPECFEM3D software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.1.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code.\\

@@

>>>>

\author{$\copyright$ Princeton University (USA) and\\
University of Pau / CNRS / INRIA (France)\\
Version 2.1 \\
"Sesame"}

@@

\noindent
If you use this new version 2.1, which has non blocking MPI for much better performance for medium or large runs, please cite at least one of these six articles,
in which results of non blocking MPI runs are presented: \cite{PeKoLuMaLeCaLeMaLiBlNiBaTr11,KoErGoMi10,KoViCh10,Kom11,CaKoLaTiMiLeSnTr08,MaKoBlLe08}.\\

@@

The SPECFEM3D software package comes in a gzipped tar ball. In the
directory in which you want to install the package, type
\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.1.0.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D/} will then contain
the source code.\\

@@

 MPI v 2.1 `Sesame' (Spectral ElementS on Any MEsh), July 2012: 
 Max Rietmann, Peter Messmer, Daniel Peter: support for CUDA GPUs. \\
